### 2020-02-12 README.Rmd
Testing.

The listdown package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized heirarchically. From the list, 
listdown creates a workflowr, pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document  with all tables and visualization that will appear. This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions.

listdown provides a reproducible means for _analytical_ document elements. It is most compatible with
data analysis pipelines where the data format is fixed but the analyses are either being updated, 
which may affect _narrative_ elements including the result discussion and conclusion, or where the
experiment is different, which affects all narrative elements.

@@

>>>>

The listdown package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized heirarchically. With the list and a listdown object a workflowr, pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document with all tables and visualization that will appear (_computational_ components). This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).

listdown provides a reproducible means for producing a document with specified computational components. It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components If the narrative components are not changing with the data being pushed through your analysis pipeline, then you may be better off writing the R Markdown code manually.

@@

## Example

As a toy example, suppose we would like to create an html document plotting Anscombe's quartet with
each plot having it's own section. To construct the document, we will need to two objects. The first
is a presentation list, whose names indicate section (or subsection) titles and whose elements are
the objects to present. The second is a `listdown` object, which describes how the object should 
be rendered in the document.

```{r eval = FALSE}
library(listdown)
library(ggplot2)

data(anscombe)

# Create the ggplot objects to display.
pres_list <- list(
  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point() + theme_bw(),
  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point() + theme_bw(),
  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point() + theme_bw(),
  `Outlier Horizontal` = ggplot(anscombe, aes(x = x4, y = y4)) + geom_point() + theme_bw())

# Save the pres_list object so that it can be used in the R Markdown document.
saveRDS(pres_list, "pres-list.rds")

# Create a listdown object.
ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the pres_list elements.

# Output an html document to a string.
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                     author = "Francis Anscombe",
                     date = "1973"),
  ld_make_chunks(pres_list, ld))

doc
```

```{r eval = TRUE, echo = FALSE}
library(listdown)
library(ggplot2)

data(anscombe)

# Create the ggplot objects to display.
pres_list <- list(
  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point() + theme_bw(),
  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point() + theme_bw(),
  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point() + theme_bw(),
  `Outlier Horizontal` = ggplot(anscombe, aes(x = x4, y = y4)) + geom_point() + theme_bw())

# Create a listdown object.
ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the plot types.

# Output an html document to a string.
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                     author = "Francis Anscombe",
                     date = "1973"),
  ld_make_chunks(pres_list, ld))

doc
```

The document can then be written to a file, rendered, and viewed with the following code.

```{r message = FALSE, eval = FALSE}
library(rmarkdown)

writeLines(doc, file("anscombe.Rmd"))
render("anscombe.Rmd")
browseURL("anscombe.html")
```
